\texttt{escheR}: Unified multi-dimensional visualizations with Gestalt principles

### 2023-05-09 Manuscript/manuscript.tex
Uncomment backmatters
Add co-authors' info

\usepackage[sort&compress,square,numbers]{natbib}
\bibliographystyle{unsrtnat}

%\setmainfont{Helvetica}
\title{\texttt{escheR}: Unified multi-dimensional visualizations with Gestalt principles}
\author[1]{Boyi Guo}
\author[1,2]{Stephanie C. Hicks\thanks{Correspondence to \url{shicks19@jhu.edu}}}
\affil[1]{Department of Biostatistics, Johns Hopkins Bloomberg School of Public Health, MD, USA}
\affil[2]{Malone Center for Engineering in Healthcare, Johns Hopkins University, MD, USA}
\date{\today}

@@

\begin{itemize}[nosep]
    \item \textbf{Boyi Guo}:  Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing, Visualization
    \item \textbf{Stephanie C. Hicks}: Conceptualization, Resources, Writing - Review \& Editing, Visualization, Supervision, Project administration, Funding acquisition
\end{itemize}

@@

\subsection*{Acknowledgements}
BG would like to acknowledge Dr. Leonardo Collado-Torres, Louise Huuki-Myers, Dr. Lukas M. Weber, and Leon Di Stefano for their helpful comments, feedback and suggestions on \texttt{escheR} functionality.

@@

\begin{itemize}[nosep]
    \item Boyi Guo (ORCiD: \href{https://orcid.org/0000-0003-2950-2349}{0000-0003-2950-2349})
    \item Stephanie C. Hicks (ORCiD: \href{https://orcid.org/0000-0002-7858-0231}{0000-0002-7858-0231})
\end{itemize}

@@

\clearpage 
% \printbibliography
\bibliography{refs}

@@

{\large Boyi Guo, Stephanie C.\ Hicks$^*$}

>>>>

\usepackage[sort&compress,square,numbers]{natbib}
\bibliographystyle{abbrv}

%\setmainfont{Helvetica}
\title{\texttt{escheR}: Unified multi-dimensional visualizations with Gestalt principles}
\author[1]{Boyi Guo}
\author[2]{Louise A. Huuki-Myers}
\author[3,4]{Melissa Grant-Peters}
\author[2]{Leonardo Collado-Torres}
\author[1,5]{Stephanie C. Hicks\thanks{Correspondence to \url{shicks19@jhu.edu}}}
\affil[1]{Department of Biostatistics, Johns Hopkins Bloomberg School of Public Health, MD, USA}
\affil[2]{Lieber Institute for Brain Development, Johns Hopkins Medical Campus, Baltimore, MD, USA}
\affil[3]{Genetics and Genomic Medicine, Great Ormond Street Institute of Child Health, University College London, London, UK}
\affil[4]{Aligning Science Across Parkinson’s (ASAP) Collaborative Research Network, Chevy Chase, MD, USA}
\affil[5]{Malone Center for Engineering in Healthcare, Johns Hopkins University, MD, USA}
\date{\today}

@@

\begin{itemize}[nosep]
    \item \textbf{Boyi Guo}:  Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing, Visualization
    \item \textbf{Louise A. Huuki-Myers}: Conceptualization, Software
    \item \textbf{Melissa Grant-Peters}: Conceptualization
    \item \textbf{Leonardo Collado-Torres}: Conceptualization, Software
    \item \textbf{Stephanie C. Hicks}: Conceptualization, Resources, Writing - Review \& Editing, Visualization, Supervision, Project administration, Funding acquisition
\end{itemize}

@@

\subsection*{Acknowledgements}
BG would like to acknowledge Kristen R. Maynard, Nicholas J. Eagles, Mina Ryten, Leon Di Stefano, and Lukas M. Weber for their helpful comments, feedback and suggestions on \texttt{escheR} functionality. Kristen R. Maynard and Nicholas J. Eagles are employed by the Lieber Institute for Brain Development (LIBD); Mina Ryten is employed by University College London; Leon Di Stefano and Lukas M. Weber are from the Johns Hopkins Bloomberg School of Public Health, Department of Biostatistics.

@@

\begin{itemize}[nosep]
    \item Boyi Guo (ORCiD: \href{https://orcid.org/0000-0003-2950-2349}{0000-0003-2950-2349})
    \item Louise A. Huuki-Myers (ORCiD: \href{https://orcid.org/0000-0001-5148-3602}{0000-0001-5148-3602})
    \item Melissa Grant-Peters (ORCiD: \href{https://orcid.org/0000-0003-0585-0971}{0000-0003-0585-0971})
    \item Leonardo Collado-Torres (ORCiD: \href{https://orcid.org/0000-0003-2140-308X}{0000-0003-2140-308X})
    \item Stephanie C. Hicks (ORCiD: \href{https://orcid.org/0000-0002-7858-0231}{0000-0002-7858-0231})
\end{itemize}

@@

% \clearpage 
\printbibliography
\bibliography{refs}

@@

{\large Boyi Guo, Louise A. Huuki-Myers, Melissa Grant-Peters, Leonardo Collado-Torres, Stephanie C.\ Hicks$^*$}
